When are Fuzzy Extractors Possible?

### 2015-02-24 info-bounds/FuzzyExtPossibility.tex
revising for eprint

\documentclass[11pt]{article}

\def\shownotes{1}
\def\blinded{0}

\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsfonts}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{framed}
\usepackage{algpseudocode}

@@

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{construction}[theorem]{Construction}

@@

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{
Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston
  University and MIT Lincoln Laboratory.}  \and Leonid
Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.}
\and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.
  Pennsylvania State University. This work performed while visiting Boston
  University's Hariri Institute for Computing.}}
}
\begin{document}
\maketitle

\begin{abstract}
Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key. A minimum condition for the security of the key is the hardness of guessing a value that is similar to the secret, because the fuzzy extractor converts such a guess to the key.
We define \emph{fuzzy min-entropy} to quantify this property of a noisy source of secrets.  Fuzzy min-entropy measures the success of the adversary when provided with \emph{only} the functionality of the fuzzy extractor, that is, the \emph{ideal} security possible from a noisy distribution.

High fuzzy min-entropy is necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required. Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy. In this work, we ask whether this challenge is inherent.  We show the following:
\begin{itemize}
\item \textbf{Sufficiency of fuzzy min-entropy:}  We construct a fuzzy extractor for each physical source with fuzzy min-entropy.  This result justifies fuzzy min-entropy as the right measure of the quality of a noisy distribution for key derivation.  Previous results considered the entropy and error tolerance of a separately and had not secured many sources with fuzzy min-entropy.  
The constructed fuzzy extractor must \emph{precisely know} the distribution of the noisy source.
\item \textbf{Cost of distributional uncertainty:}  High entropy sources can never be fully observed and must be modeled.  An adversary may have a better model than the fuzzy extractor designer.  To compensate, fuzzy extractors are typically designed to work for families of physical sources. We build a family of high fuzzy min-entropy sources which no fuzzy extractor can secure.  This result emphasizes the importance of high fidelity models of high entropy sources.
\end{itemize}
We provide similar but stronger results for secure sketches, whose goal is not to derive a consistent key, but to recover a consistent reading of the secret.  Our results are information-theoretic, but we discuss implications for the computational setting.

@@

The noninteractive setting is modeled by a primitive called a fuzzy extractor~\cite{DBLP:journals/siamcomp/DodisORS08}, which consists of two algorithms.  %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.   T
The  generate algorithm ($\gen$)  takes an initial reading $w$ and produces an output $\key$ along with a nonsecret helper value $p$.  The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.   The correctness guarantee is that the key is reproduced precisely when the distance between $w$ and $w'$ is at most $t$.

@@

\paragraph{Fuzzy Min-Entropy}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting the security of $\key$ by running $\rep$. Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within the ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.  Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \ge \Hfuzz(W) \ge \Hoo(W)-\log |B_t|$.

Fuzzy min-entropy measures the quality of a distribution when provided oracle access to the functionality of a fuzzy extractor.  Fuzzy min-entropy measures the ideal security of a noisy source of entropy when used for key derivation, similar to distributional notions of program obfuscation~\cite{barak2001possibility,DBLP:conf/stoc/DodisS05,DBLP:conf/tcc/DodisS05}---we discuss the connection in \secref{sec:related settings}.  Superlogarithmic fuzzy min-entropy is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition).

However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.\footnote{For nearly uniform distributions, $\Hfuzz(W) \approx \Hoo(W)- \log |B_t|$.  In this setting, standard coding based constructions of fuzzy extractors (instantiated with optimum codes) yield keys of size approximately $\Hfuzz(W)$.}  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}. We provide an answer in two settings.

\paragraph{Sufficiency of $\Hfuzz(W)$ for a Precisely Known Distribution}
Ideally, a fuzzy extractor has \emph{precise knowledge} of the probability distribution function of $W$.  We call this  the \emph{precise knowledge} setting.  In this setting, we show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}). Our construction crucially utilizes the probability distribution function of $W$ and, in particular, is not polynomial time.  This result shows that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor of a distribution $W$.

A number of previous works in the precise knowledge setting have provided efficient algorithms and
tight bounds for specific distributions---generally the uniform distribution or
i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining,DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
Our characterization unifies previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.

\paragraph{The Challenge of Precisely Distributional Knowledge}
Assuming \emph{precise knowledge} of a distribution $W$ may be unrealistic. Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled. It is imprudent to assume that the designer's model of a distribution is completely accurate---the adversary, with greater resources, would likely be able to build a better model. Therefore, fuzzy extractor designs cannot usually be tailored to one  particular source. Existing designs work for a family of sources (for example, all sources of min-entropy at least $m$ with at most $t$ errors). Thus, the design is fixed with a partially known distribution, and the adversary may know more about the distribution than the designer of the fuzzy extractor.  We call this the \emph{distributional uncertainty} setting.

@@

\paragraph{Stronger Results on Information Reconciliation (Secure Sketches)}
Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$), followed by randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.  The security losses incurred in the first of these two steps dominate for typical sources and, indeed, this step is less well understood.\footnote{Randomness extractors have matching upper and lower bounds on the security loss: for every extra two bits of output key, they lose one bit of security} Formally, a secure sketch performs non-interactive information reconciliation via pair of algorithms: $\sketch$ takes $w$ and produces a nonsecret value $ss$, while $\rec$ takes a value $w'$ within distance $t$ of $w$ and uses $\sketch$ to output the original reading $w$.

We show comparable, but stronger, results for secure sketches.  Namely, we show in \corref{cor:extension to fuzz ext} that secure sketches are possible if the distribution $W$ is precisely known. (In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by applying a randomness extractor.)

On the other hand, there is a family of sources, $\mathcal{W}_Z$, where each element has $\Hfuzz(W_z)=\Hoo(W_z) = \omega(\log n)$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}). The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).

\paragraph{Interpreting our Results}
Our results show that fuzzy min-entropy is sufficient for noisy key derivation if the distribution is precisely known but insufficient if the distribution is only known to come from a family.  A similar situation occurs in the (noiseless) randomness extraction literature~\cite{nisan1993randomness}.  Deterministic randomness extractors are possible if the distribution is precisely known, but impossible for all high min-entropy distributions~\cite{santha1986generating}.  This impossibility can be overcome by the use of a short seed of uniform randomness.  
We must find an analogous relaxation to derive keys from noisy sources.  One natural relaxation is providing security against only  computationally bounded adversaries, see \secref{sec:related settings}.

@@

\paragraph{Techniques for Positive Results for a Precisely Known Distribution} We now explain how to construct a secure sketch for a precisely known distribution $W$ with fuzzy min-entropy (we already explained how to construct a fuzzy extractor from it).  We begin with distributions in which all points in the support have the same probability (so-called ``flat'' distributions).   Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must disambiguate which point $w\in W$ within distance $t$ of $w'$ was sketched. Disambiguating multiple points can be accomplished by universal hashing, as long as the size of hash output space is slightly greater than the number of possible points. Thus, our sketch is computed via a universal hash of $w$. To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$. Because the distribution is flat, it is also the ball with the most points of nonzero probability. Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball. Since $\Hfuzz(W)$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.

@@

\subsection{Related Settings}
\label{sec:related settings}
\paragraph{Other settings with close readings:  $\Hfuzz$ is sufficient}
The security definition of fuzzy extractors and secure sketches can be weakened to protect only against computationally bounded adversaries~\cite{fuller2013computational}.   In this computational setting, a single fuzzy extractor (or secure sketch) can simultaneously secure all possible distributions by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}. The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.\footnote{If this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).}  This construction is secure when the adversary can rarely learn \key with oracle access to the program functionality.  The set of distributions with fuzzy min-entropy are exactly those where an adversary learns \key with oracle access to the functionality with negligible probability. Thus, extending our negative result to the computational setting would rule out the existence of semantically-secure multilinear maps.

Furthermore, the functional definition of fuzzy extractors and secure sketches can be weakened to permit interaction between the party having $w$ and the party having $w'$. Such a weakening is useful for secure remote authentication~\cite{Boyen05secureremote}. When both interaction and computational assumptions are allowed, secure two-party computation can produce a key that will be secure whenever the distribution $W$ has fuzzy min-entropy.  The two-party computation protocol needs to be secure without assuming authenticated channels; it can be built under the assumptions that collision-resistant hash functions and enhanced trapdoor permutations exist~\cite{DBLP:journals/joc/BarakCLPR11}.

@@

Note that we have no requirement that the algorithms are compact or efficient, and so the distribution can be fully known to them. Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.

@@

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{2.5in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item Sample $K\leftarrow \mathcal{K}$.
\item Set $ss = F(K, w), K$.
\end{enumerate}
\vspace{.3in}
\end{minipage} &
\begin{minipage}{3.5in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', ss =( y, K))$
\item Let $W^* = \{w \in \supp(W) | \dis(w, w')\le t\}$.
\item For $w^*\in W^*$, if $F(K, w^*) = y$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

\begin{lemma}
\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, \{W\}, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
\end{lemma}
\begin{corollary}
Let $n = \log |\mathcal{M}|$.  If $|R| \ge |\beta_{t}|\cdot n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log \beta_{t} + \omega(\log n)$ suffices.
\end{corollary}

\noindent
\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is $\Hav(W |\sketch(W)) = \Hoo(W) - \log \beta_{t} -\log 1/\delta$. For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). By choosing $\delta$ based on $\Hfuzz(W)$ we build $(\sketch, \rec)$ such that $\Hav(W | \sketch(W)) = \omega(\log n)$.

@@

We prove impossibility in a game that is harder for the adversary to win: 1) the challenger specifies $(\sketch, \rec)$ 2) the adversary samples a random distribution from $W_z\leftarrow \mathcal{W}_Z$ 3) the adversary wins if $\Hav(W_z|\sketch(W_z)) < \tilde{m}$.\footnote{Our results rule out security for an average member of $\mathcal{W}$.  It may be possible to improve parameters by ruling out only a worst case $W$.  In \apref{sec:def equiv}, we show that providing security for a family $\mathcal{W}$ is equivalent to providing security for all distributions over that family.}

>>>>

\def\shownotes{0}
\def\blinded{0}
\def\lncs{0}

\ifnum\lncs=0
	\documentclass[11pt]{article}
	\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
	\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
	%\geometry{landscape}                % Activate for for rotated page geometry
	%\usepackage[parfill]{parskip}
	\usepackage{amsthm}
	\newtheorem{theorem}{Theorem}[section]
	\newtheorem{lemma}[theorem]{Lemma}
	\newtheorem{proposition}[theorem]{Proposition}
	\newtheorem{corollary}[theorem]{Corollary}
	\newtheorem{definition}[theorem]{Definition}
	\newtheorem{assumption}[theorem]{Assumption}
	\newtheorem{claim}[theorem]{Claim}
	\newtheorem{problem}[theorem]{Problem}
	\newtheorem{construction}[theorem]{Construction}

\else
	\documentclass[runningheads]{llncs}
	\newtheorem{construction}{Construction}
\fi

\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsfonts}
%\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{framed}
\usepackage{algpseudocode}

@@

%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{claim}[theorem]{Claim}
%\newtheorem{problem}[theorem]{Problem}
%\newtheorem{construction}[theorem]{Construction}

@@

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{
Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston
  University and MIT Lincoln Laboratory.}  \and Leonid
Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.}
\and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.
  Pennsylvania State University. This work performed while visiting Boston
  University's Hariri Institute for Computing.}}
}
%\author{}\institute{}
\begin{document}
\maketitle

\begin{abstract}
Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy
readings of a high-entropy secret into the same uniformly distributed
key. A minimum condition for the security of the key is the hardness
of guessing a value that is similar to the secret, because the fuzzy
extractor converts such a guess to the key.

\smallskip
We define \emph{fuzzy min-entropy} to quantify this property of a noisy source of secrets.  Fuzzy min-entropy measures the success of the adversary when provided with \emph{only} the functionality of the fuzzy extractor, that is, the \emph{ideal} security possible from a noisy distribution.  
High fuzzy min-entropy is necessary for the existence of a fuzzy
extractor. 
\smallskip

We ask: \emph{is high fuzzy min-entropy a
  sufficient condition for key extraction from noisy sources?}
If only computational security is required, recent progress on program
obfuscation gives evidence that fuzzy
min-entropy is indeed sufficient. In contrast,
information-theoretic fuzzy extractors are not known for many
practically relevant sources of high fuzzy min-entropy. 
\smallskip

In this paper, we show that fuzzy min-entropy is also sufficient for
information-theoretically secure fuzzy extraction. For every source
distribution $W$ for which security is possible we give a secure fuzzy
extractor.

\smallskip
Our construction relies on the fuzzy extractor knowing the precise
distribution of the source $W$.  A more ambitious goal is to design a
single extractor that works for all possible sources.  We show that
this more ambitious goal is impossible: we give a family of sources
with high fuzzy min-entropy for which no single fuzzy extractor is
secure.  This result emphasizes the importance of accurate models
of high entropy sources.

% \begin{itemize}
% \item \textbf{Sufficiency of fuzzy min-entropy:} We show that for each
%   source with nontrivial (that is, $\omega(\log n)$) fuzzy min-entropy,
%   there is an infor\-mation-theoretic fuzzy extractor that reliably
%   extracts a key of length roughly the fuzzy min-entropy.  This result
%   justifies fuzzy min-entropy as the ``right'' measure of the quality
%   of a noisy distribution for key derivation. Previous results
%   considered the entropy and error tolerance of a source separately;
%   consequently, for many sources with high fuzzy min-entropy, existing
%   constructions did not lead to secure fuzzy extractors.

%   Our construction works for every source, but requires
%   \emph{precise knowledge} of the distribution of the source.

% \item \textbf{Cost of distributional uncertainty:} A more ambitious
%   goal is to design a single extractor that works for all possible
%   sources.

% High entropy
%   sources can never be fully observed by sampling, and so some
%   modeling assumptions must be used.

% Moreover,  An
%   adversary may have a better model than the fuzzy extractor designer.
%   To compensate, fuzzy extractors are typically designed to work for
%   families of physical sources. We build a family of high fuzzy
%   min-entropy sources which no fuzzy extractor can secure.  This
%   result emphasizes the importance of high fidelity models of high
%   entropy sources.
% \end{itemize}
% We provide similar but stronger results for secure sketches, whose goal is not to derive a consistent key, but to recover a consistent reading of the secret.  Our results are information-theoretic, but we discuss implications for the computational setting.

@@

The noninteractive setting is modeled by a primitive called a fuzzy extractor~\cite{DBLP:journals/siamcomp/DodisORS08}, which consists of two algorithms.  %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.   T
The  generate algorithm ($\gen$)  takes an initial reading $w$ and produces an output $\key$ along with a nonsecret helper value $p$.  The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.   The correctness guarantee is that the \key is reproduced precisely when the distance between $w$ and $w'$ is at most $t$.

@@

\paragraph{Fuzzy Min-Entropy}
We introduce a new entropy notion that precisely measures how hard it
is for the adversary to guess a value within distance $t$ of the
original reading $w$. 
Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within the ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.  Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \ge \Hfuzz(W) \ge \Hoo(W)-\log |B_t|$.

% Fuzzy min-entropy measures the quality of a distribution when provided oracle access to the functionality of a fuzzy extractor.  
Fuzzy min-entropy measures the ideal security of a noisy source of
entropy when used for key derivation, similar to distributional
notions of program obfuscation
(e.g.,~\cite{barak2001possibility,DBLP:conf/stoc/DodisS05,DBLP:conf/tcc/DodisS05};
see \secref{sec:related settings} for discussion).  Superlogarithmic fuzzy min-entropy is \emph{necessary} for nontrivial key extraction~(Proposition \ref{prop:fuzz necessary}).

However, existing constructions do not measure their security in terms
of fuzzy min-entropy; instead, their security is shown to be
$\Hoo(W)$ minus some loss, for error-tolerance, that is at least $\log |B_t|$. Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.\footnote{For nearly uniform distributions, $\Hfuzz(W) \approx \Hoo(W)- \log |B_t|$.  In this setting, standard coding based constructions of fuzzy extractors (instantiated with optimum codes) yield keys of size approximately $\Hfuzz(W)$.}  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}. We provide an answer in two settings.

\paragraph{Sufficiency of $\Hfuzz(W)$ for a Precisely Known Distribution}
Ideally, a fuzzy extractor has \emph{precise knowledge} of the
probability distribution function of $W$.  We call this  the
\emph{precise knowledge} setting.  In this setting, we show that for
every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to
construct a fuzzy extractor with a superlogarithmic length $\key$
(\corref{cor:extension to fuzz ext}). Our construction crucially
utilizes the probability distribution function of $W$ and, in
particular, is not polynomial time.  This result shows that
$\Hfuzz(W)$ is a necessary and sufficient condition for building a
fuzzy extractor for a given distribution $W$.

A number of previous works in the precise knowledge setting have provided efficient algorithms and
tight bounds for specific distributions---generally the uniform distribution or
i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining}, \cite{DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
Our characterization unifies previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.

\paragraph{The Challenge of Precise Distributional Knowledge}
Assuming precise knowledge of a distribution $W$ may be unrealistic. Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled. It is imprudent to assume that the designer's model of a distribution is completely accurate---the adversary, with greater resources, would likely be able to build a better model. Therefore, fuzzy extractor designs cannot usually be tailored to one  particular source. Existing designs work for a family of sources (for example, all sources of min-entropy at least $m$ with at most $t$ errors). Thus, the design is fixed with a partially known distribution, and the adversary may know more about the distribution than the designer of the fuzzy extractor.  We call this the \emph{distributional uncertainty} setting.

@@

\paragraph{Stronger Results on Information Reconciliation (Secure Sketches)}
Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$), followed by randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.  The security losses incurred in the first of these two steps dominate for typical sources and, indeed, this step is less well understood.\footnote{Randomness extractors have matching upper and lower bounds on the security loss: for every extra two bits of output key, they lose one bit of security} Formally, a secure sketch performs non-interactive information reconciliation via pair of algorithms: $\sketch$ takes $w$ and produces a nonsecret value $ss$, while $\rec$ takes a value $w'$ within distance $t$ of $w$ and uses $ss$ to output the original reading $w$.

For secure sketches, we show results that are similar to but
stronger than our results for fuzzy extractors.  Namely, we show in \corref{cor:extension to fuzz ext} that secure sketches are possible if the distribution $W$ is precisely known. (In fact, we obtain our fuzzy extractors for the case of a precisely known distribution from this result by applying a randomness extractor.)

On the other hand, there is a family of sources, $\mathcal{W}_Z$,
where each element has $\Hfuzz(W_z)=\Hoo(W_z) = \omega(\log n)$ for
which no secure sketch correcting even a few errors is
possible~(\thref{thm:imposs sketch}). The impossibility result applies
even when $\rec$ is allowed to be incorrect with probability up to
$1/4$ (in contrast to our fuzzy extractor impossibility result, which
requires perfect reconstruction).

% \paragraph{Interpreting our Results}
% Our results show that fuzzy min-entropy is necessary and sufficient for noisy key
% derivation if the distribution is precisely known. We give evidence
% that fuzzy min-entropy alone is not sufficient when the exact
% distribution is uncertain.  
%  % but insufficient if the distribution is only known to come from a
%  % family. 
%  A similar situation occurs in the (noiseless) randomness extraction literature~\cite{nisan1993randomness}.  Deterministic randomness extractors are possible if the distribution is precisely known, but impossible for all high min-entropy distributions~\cite{santha1986generating}.  This impossibility can be overcome by the use of a short seed of uniform randomness.  
% We must find an analogous relaxation to derive keys from noisy sources.  One natural relaxation is providing security against only  computationally bounded adversaries, see \secref{sec:related settings}.

@@

\paragraph{Techniques for Positive Results for a Precisely Known
  Distribution} 
We now explain how to construct a secure sketch for a precisely known
distribution $W$ with fuzzy min-entropy (we already explained how to
construct a fuzzy extractor from it).  We begin with distributions in
which all points in the support have the same probability (so-called
``flat'' distributions).  Consider some subsequent reading $w'$. To
achieve correctness, the sketch algorithm must disambiguate which
point $w\in W$ within distance $t$ of $w'$ was
sketched. Disambiguating multiple points can be accomplished by
universal hashing, as long as the size of hash output space is
slightly greater than the number of possible points. Thus, our sketch
is computed via a universal hash of $w$. To determine the length of
that sketch, consider the heaviest (according to $W$) ball $B^*$ of radius
$t$. Because the distribution is flat, $B^*$ is also the ball with the
most points of nonzero probability. Thus, the length of the sketch
needs to be slightly greater than the logarithm of the number of
non-zero probability points in $B^*$. Since $\Hfuzz(W)$ is
determined by the weight of $B^*$, the number of points cannot be
too high and there will be remaining entropy after the sketch is published.
This remaining entropy suffices to extract a key.

@@

\subsection{Related Settings}
\label{sec:related settings}
\paragraph{Other settings with close readings:  $\Hfuzz$ is sufficient}
The security definition of fuzzy extractors and secure sketches can be weakened to protect only against computationally bounded adversaries~\cite{fuller2013computational}.   In this computational setting, a single fuzzy extractor (or secure sketch) can simultaneously secure all possible distributions by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}. The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.\footnote{If this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).}  This construction is secure when the adversary can rarely learn \key with oracle access to the program functionality.  This is true for the set of distributions  with fuzzy min-entropy~(and only those distributions). Thus, extending our negative result to the computational setting would rule out the existence of virtual grey-box obfuscation for all circuits.

Furthermore, the functional definition of fuzzy extractors and secure sketches can be weakened to permit interaction between the party having $w$ and the party having $w'$. Such a weakening is useful for secure remote authentication~\cite{Boyen05secureremote}. When both interaction and computational assumptions are allowed, secure two-party computation can produce a key that will be secure whenever the distribution $W$ has fuzzy min-entropy.  The two-party computation protocol needs to be secure without assuming authenticated channels; it can be assuming the existence of collision-resistant hash functions and enhanced trapdoor permutations~\cite{DBLP:journals/joc/BarakCLPR11}.

@@

Note that we have no requirement that the algorithms are compact or efficient, and so the distribution can be fully known to them. Finding a natural model of specifying distributions that allows for efficient~(yet generic) constructions of sketches and extractors for a precisely known distribution is an interesting problem.

@@

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{1.8in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item Sample $K\leftarrow \mathcal{K}$.
\item Set $ss = F(K, w), K$.
\end{enumerate}
\vspace{.3in}
\end{minipage} &
\begin{minipage}{3.5in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', ss =( y, K))$
\item Let $W^* = \{w \in \supp(W) | \dis(w, w')\le t\}$.
\item For $w^*\in W^*$, if $F(K, w^*) = y$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

\begin{lemma}
\label{lem:flat hashing}
Let $W$ be a flat with $\Hoo(W)\ge m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, \{W\}, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
\end{lemma}
\begin{proof}
We first argue security.  Fix some $W\in\mathcal{W}$. Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.  Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(\mathcal{K}, W)) \ge \Hoo(W) - \log |F(\mathcal{W}, W)| \ge m - \log |R|$.

\noindent
We now argue correctness.  Fix some $w, w'$.  Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$.  The size of $W^*$ is at most $\beta_{t}$.  Since $w, w'$ are independent of $\sketch$ this set is independent of the choice of $\mathcal{K}$.  The algorithm  $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ collides is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w &\wedge F(K, w^*) = F(K, w)] \\&\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{\beta_{t}-1}{|R|}
\end{align*}
The inequality proceeds by union bound. The first equality proceeds by the universality of $F$ and the second inequality proceeds by noting the number of wrong neighbors is bounded by $\beta_{t}-1$.  This completes the proof.
\end{proof}

%\noindent
%\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is $\Hav(W |\sketch(W)) = \Hoo(W) - \log \beta_{t} -\log 1/\delta$. For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). By choosing $\delta$ based on $\Hfuzz(W)$ we build $(\sketch, \rec)$ such that $\Hav(W | \sketch(W)) = \omega(\log n)$.

@@

We prove impossibility in a game that is harder for the adversary to win: 1) the challenger specifies $(\sketch, \rec)$ 2) the adversary randomly samples $W_z\leftarrow \mathcal{W}_Z$ 3) the adversary wins if $\Hav(W_z|\sketch(W_z ) ) < \tilde{m}$.\footnote{Our results rule out security for an average member of $\mathcal{W}_Z$.  It may be possible to improve parameters by ruling out only a worst case $W_z$.  In \apref{sec:def equiv}, we show that providing security for the set of distributions $\mathcal{W}_Z$ is equivalent to providing security for all distributions $Z$ over that family.}

Let $V$ be the process of uniformly sampling $W_z\leftarrow \mathcal{W}_Z$ and then sampling $w\leftarrow W_z$.  Let the random variable $Z$ represent the process of sampling $W_z\leftarrow \mathcal{W}_Z$.  The view of the challenger is $V$, while the view of the adversary is $\sketch(V)$ and $Z$. 
We now show a family of distributions $\mathcal{W}_Z$ that does not admit a secure sketch.
